### 2015-12-11 paper/4-performance.tex
Added two benchmark models already; still drafts from various sources, so should update them
Added phold model, again a draft from elsewhere
Gave figures a more explicit name
Added all necessary plots, but some are not yet completely correct or in-depth enough
fixed a few typos changed compile flags to include -flto

We start of with a comparison of sequential simulation, to show how adevs and dxex relate in this simple case.
We not only show that our approach does not influence performance negatively, but also that our main simulation algorithm, similar to the one of PythonPDEVS, is significantly faster than the one found in adevs.
Similar differences, compared to adevs, can also be seen in the parallel simulation benchmarks.
In the parallel simulation benchmarks, the benefit of our different synchronization protocols is also indicated.

For all benchmarks, results were all well within 1\% deviation of the average, such that only the average is used in the remainder of this section.
The same compilation flags were used for both adevs and dxex benchmarks (``\texttt{-O3}'').
To guarantee comparable results, no IO was performed during the benchmarking phase.
Simulation traces were used to verify that both adevs and dxex models have exactly the same behaviour.
All benchmarks were performed using Linux, but our simulation tool works equally well on Windows and Mac.

@@

\begin{figure}
    \center
    %TODO
    %\includegraphics[width=\columnwidth]{fig/queue_model.eps}
    \caption{Queue model for depth 3 and width 2.}
    \label{fig:queue_model}

    %TODO
    %\includegraphics[width=\columnwidth]{fig/interconnect_model.eps}
    \caption{HighInterconnect model for four models.}
    \label{fig:interconnect_model}

    %TODO
    %\includegraphics[width=\columnwidth]{fig/PHOLD_model.eps}
    \caption{PHOLD model for four models, split over two nodes. In parallel simulation, each coupled model is simulated at a different node.}
    \label{fig:PHOLD_model}
\end{figure}

@@

\begin{figure}
	\includegraphics[width=\columnwidth]{fig/fig1.eps}
	\caption{Queue benchmark results for sequential simulation.}
	\label{fig:Queue_benchmark}
\end{figure}

@@

%TODO only include sequential results?
\begin{figure}
	\includegraphics[width=\columnwidth]{fig/fig3.eps}
	\caption{Interconnect benchmark results for sequential simulation.}
	\label{fig:Interconnect_benchmark}
\end{figure}

@@

Similar to the sequential benchmarks, Figure~\ref{fig:queue_benchmark_parallel} shows that dxex again outperforms adevs, using both optimistic and conservative synchronization.
%TODO wait for raw results to make conclusions
Behaviour is exactly the same as in sequential simulation, but some speedup is achieved.
In this case, conservative synchronization seems to be better than optimistic synchronization, at the cost of providing the lookahead.

\begin{figure}
	\includegraphics[width=\columnwidth]{fig/fig2.eps}
	\caption{Queue benchmark results for parallel simulation using 4 cores.}
	\label{fig:queue_benchmark_parallel}
\end{figure}

@@

@@

\begin{figure}
    \includegraphics[width=\columnwidth]{fig/phold_voorlopig.eps}
    \caption{Phold benchmark results with high-priority events.}
    \label{fig:phold_priority}
\end{figure}

@@

\begin{figure}
    %TODO
    %\includegraphics[width=\columnwidth]{fig/interconnect_parallel.eps}
    \caption{Interconnect benchmark results for parallel simulation.}
    \label{fig:interconnect_benchmark_parallel}
\end{figure}

>>>>

We start off with a comparison of sequential simulation, to show how adevs and dxex relate in this simple case.
We not only show that our approach does not influence performance negatively, but also that our main simulation algorithm, similar to the one of PythonPDEVS, is significantly faster than the one found in adevs.
Similar differences, compared to adevs, can also be seen in the parallel simulation benchmarks.
In the parallel simulation benchmarks, the benefit of our different synchronization protocols is also indicated.

For all benchmarks, results were all well within 1\% deviation of the average, such that only the average is used in the remainder of this section.
The same compilation flags were used for both adevs and dxex benchmarks (``\texttt{-O3 -flto}'').
To guarantee comparable results, no IO was performed during the benchmarking phase.
Simulation traces were used to verify that both adevs and dxex models have exactly the same behaviour.
All benchmarks were performed using Linux, but our simulation tool works equally well on Windows and Mac.

@@

\begin{figure}
    \center
    \includegraphics[width=\columnwidth]{fig/queue_model.pdf}
    \caption{Queue model for depth 3 and width 2.}
    \label{fig:queue_model}
\end{figure}

\begin{figure}
    \center
    \includegraphics[width=\columnwidth]{fig/interconnect_model.pdf}
    \caption{HighInterconnect model for four models.}
    \label{fig:interconnect_model}
\end{figure}

\begin{figure}
    \center
    \includegraphics[width=0.5\columnwidth]{fig/phold_model.pdf}
    \caption{PHOLD model for four models, split over two nodes. In parallel simulation, each coupled model is simulated at a different node.}
    \label{fig:PHOLD_model}
\end{figure}

@@

\begin{figure}
	\includegraphics[width=\columnwidth]{fig/queue_sequential.eps}
	\caption{Queue benchmark results for sequential simulation.}
	\label{fig:Queue_benchmark}
\end{figure}

@@

\begin{figure}
	\includegraphics[width=\columnwidth]{fig/interconnect_sequential.eps}
	\caption{Interconnect benchmark results for sequential simulation.}
	\label{fig:Interconnect_benchmark}
\end{figure}

@@

Similar to the sequential benchmarks, Figure~\ref{fig:queue_benchmark_parallel} shows that dxex again outperforms adevs, using both optimistic and conservative synchronization.
Behaviour is exactly the same as in sequential simulation, but some speedup is achieved.
In this case, conservative synchronization seems to be better than optimistic synchronization, at the cost of providing the lookahead.

\begin{figure}
	\includegraphics[width=\columnwidth]{fig/queue_parallel.eps}
	\caption{Queue benchmark results for parallel simulation using 4 cores.}
	\label{fig:queue_benchmark_parallel}
\end{figure}

@@

\begin{figure}
    \includegraphics[width=\columnwidth]{fig/phold_remotes.eps}
    \caption{Phold benchmark results for parallel simulation using 4 cores, with varying fraction of remote events.}
\end{figure}

@@

\begin{figure}
    \includegraphics[width=\columnwidth]{fig/phold_voorlopig.eps}
    \caption{Phold benchmark results for parallel simulation using 4 cores, with varying amount of high-priority events.}
    \label{fig:phold_priority}
\end{figure}

@@

\begin{figure}
    \includegraphics[width=\columnwidth]{fig/interconnect_parallel.eps}
    \caption{Interconnect benchmark results for parallel simulation.}
    \label{fig:interconnect_benchmark_parallel}
\end{figure}
